---
title: "TBM"
author: "Mostafa Kamal"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    fig_width: 8
    fig_caption: yes
---


### loading the data



```{r}
# library()

library(readxl)
library(tidyverse)
library(stargazer)
library(ggplot2)
library(plm)
library(urca)


```

```{r}

# loading the data and grooming the data
data <- read_excel("Data for analysis.xlsx", 
                                        sheet = "Final", 
                                        col_types = c(rep("text",5), rep('numeric',31)))
data <- as.data.frame(na.omit(data))



```


### Preparing the initial graphs

```{r}

# 1st one ------------------------------------------------------------------------

# for all

data %>% 
  #group_by(countryOfOrigin) %>% 
  ggplot(mapping = aes(x=TA_TE, y=FundingCost))+
  geom_point()+
  geom_smooth(method = 'lm', se=FALSE)+
  #facet_wrap(facets = ~countryOfOrigin, scales = 'free_y', ncol = 2)+
  labs(title = "Cost of Debt Funding",
       # subtitle = "Categories are based on bank regions",
       caption = "Data source: Bloomberg") +
  xlab('Total Asset/Total Equity') + ylab('Funding Cost')+
  theme(legend.position = 'none',
        plot.caption = element_text(hjust = 0))

# for country wise

data %>% 
  group_by(countryOfOrigin) %>% 
  ggplot(mapping = aes(x=TA_TE, y=FundingCost,col=countryOfOrigin))+
  geom_point()+
  geom_smooth(method = 'lm', se=FALSE)+
  facet_wrap(facets = ~countryOfOrigin, scales = 'free_y', ncol = 2)+
  labs(title = "Cost of Debt Funding",
       subtitle = "Categories are based on bank regions",
       caption = "Data source: Bloomberg") +
  xlab('Total Asset/Total Equity') + ylab('Funding Cost')+
  theme(legend.position = 'none',
        plot.caption = element_text(hjust = 0))



```



```{r}

# 2nd one ------------------------------------------------------------------------

# for all 

data %>% 
  # group_by(countryOfOrigin) %>% 
  ggplot(mapping = aes(x=TA_TE, y=TFundGrow))+
  geom_point()+
  geom_smooth(method = 'lm', se=FALSE)+
  # facet_wrap(facets = ~countryOfOrigin, scales = 'free_y', ncol = 2)+
  labs(title = "Debt Funding",
       # subtitle = "Categories are based on bank regions",
       caption = "Data source: Bloomberg") +
  xlab('Total Asset/Total Equity') + ylab('Non-equity funding Growth')+
  theme(legend.position = 'none',
        plot.caption = element_text(hjust = 0))

# for country wise

data %>% 
  group_by(countryOfOrigin) %>% 
  ggplot(mapping = aes(x=TA_TE, y=TFundGrow,col=countryOfOrigin))+
  geom_point()+
  geom_smooth(method = 'lm', se=FALSE)+
  facet_wrap(facets = ~countryOfOrigin, scales = 'free_y', ncol = 2)+
  labs(title = "Debt Funding",
       subtitle = "Categories are based on bank regions",
       caption = "Data source: Bloomberg") +
  xlab('Total Asset/Total Equity') + ylab('Non-equity funding Growth')+
  theme(legend.position = 'none',
        plot.caption = element_text(hjust = 0))


```

```{r}


# 3rd ----------------------------------------------------------------------------

# for all()

data %>% 
  # group_by(countryOfOrigin) %>% 
  ggplot(mapping = aes(x=TA_TE, y=LG))+
  geom_point()+
  geom_smooth(method = 'lm', se=FALSE)+
  # facet_wrap(facets = ~countryOfOrigin, scales = 'free_y', ncol = 2)+
  labs(title = "Lending",
       # subtitle = "Categories are based on bank regions",
       caption = "Data source: Bloomberg") +
  xlab('Total Asset/Total Equity') + ylab('Non-equity Financing Growth')+
  theme(legend.position = 'none',
        plot.caption = element_text(hjust = 0))

# for country wise

data %>% 
  group_by(countryOfOrigin) %>% 
  ggplot(mapping = aes(x=TA_TE, y=LG,col=countryOfOrigin))+
  geom_point()+
  geom_smooth(method = 'lm', se=FALSE)+
  facet_wrap(facets = ~countryOfOrigin, scales = 'free_y', ncol = 2)+
  labs(title = "Lending",
       subtitle = "Categories are based on bank regions",
       caption = "Data source: Bloomberg") +
  xlab('Total Asset/Total Equity') + ylab('Non-equity Financing Growth')+
  theme(legend.position = 'none',
        plot.caption = element_text(hjust = 0))


```


### Summary statistics 

```{r}
# High Levered and low levered banks and their summary stats

# summary statistics for the banks (need to add all the variables)

leverdUnleverd <- data %>% 
  group_by(bankName) %>% 
  summarise(
    N = n(),
    Min = min(TA_TE),
    Mean = mean(TA_TE),
    q1 = quantile(TA_TE,probs = 0.25),
    Median = median(TA_TE),
    q3 = quantile(TA_TE,probs = 0.75),
    Max = max(TA_TE))



# 1st and 4th quantile of the overall asset/equity

data %>% 
  summarise(
    quantile = quantile(TA_TE, probs = c(0.25,0.75))
  )

# finding the levered and unlevered firms

leverdUnleverd %>% 
  filter(q1<=10.11 | q1>=20.12) %>% 
  arrange(q1)


# partioning the data in the highly levered and lower levered dataset

dataHL <- data %>% 
  # select(bankName, Year, LL, HL) %>% 
  mutate(
    LL = case_when(
      bankName== "Santander Holdings"~1,
      bankName== "Capial One Financial"~1,
      bankName== "Truist Financial"~1,
      bankName== "M&T Bank"~1,
      bankName== "PNC"~1,
      bankName== "Fifth Third Bancorp"~1,
      bankName== "Bank of New York Mellon"~1,
      bankName== "KeyCorp"~1,
      bankName== "Bank of America"~1,
      bankName== "US Bancorp"~1,
      bankName== "Citigroup Inc"~1,
      TRUE ~ 0),
    HL = case_when(
      bankName== "Barclays"~1,
      bankName== "Commerzbank"~1,
      bankName== "Deutsche Bank"~1,
      TRUE ~ 0)) 

dataHL %>% 
  # group_by(LL,HL) %>% 
  filter(HL==1 | LL==1) %>%
  group_by(LL,HL) %>%
  summarise(
    obs=n(),
    assets=mean(TA/1000),
    costOfDebtFinancing = mean(FundingCost),
    growthRateOfDebtFinancing =mean(TFundGrow),
    growthRateOfLending = mean(LG),
    assetRisk = sd(TA/1000),
    ROA = mean(ROA))%>% 
  t() %>% 
  round(digits = 3)



```

```{r}

# summary statistics for all the variables

summData <- as.matrix(data[,6:dim(data)[2]]) # just numeric variables
summaryResults <- list()

allMin <- apply(summData, MARGIN = 2, FUN = min, na.rm=TRUE)
allMean <- apply(summData, MARGIN = 2, FUN = mean, na.rm=TRUE)
allMax <- apply(summData, MARGIN = 2, FUN = max, na.rm=TRUE)
allSD <- apply(summData, MARGIN = 2, FUN = sd, na.rm=TRUE)
allCorr <- round(cor(summData[,-c(1:4)]),digits = 4) # maybe a heatmap
summaryResults$All <- round(data.frame(allMin,allMean,allMax,allSD), digits = 3)


```

### Need to calculate panel wise summary (country and year wise)
### correlation heatmap


### Book of envelop calc and their figures

```{r}

# Asset and total equity (i)

dataFig <- data
dataFig$year <- as.numeric(dataFig$year)

dataFig %>% 
  group_by(year) %>% 
  summarise(
    `Median`=median(TA_TE),
    `25th Percentile` = quantile(TA_TE, probs = 0.25),
    `75th Percentile` = quantile(TA_TE, probs = 0.75)
  ) %>% 
  ungroup() %>% 
  pivot_longer(cols = -year,names_to = "variable",values_to = "value") %>% 
  ggplot(mapping = aes(x=year, y=value, col=variable))+
  geom_line()+
  ylim(c(8,30))+
  theme_bw()+
  xlab('')+
  ylab('')
  

# RWA and TierCap (i)

dataFig %>% 
  group_by(year) %>% 
  summarise(
    `Median`=median(RWA_TierCap),
    `25th Percentile` = quantile(RWA_TierCap, probs = 0.25),
    `75th Percentile` = quantile(RWA_TierCap, probs = 0.75)
  ) %>% 
  ungroup() %>% 
  pivot_longer(cols = -year,names_to = "variable",values_to = "value") %>% 
  ggplot(mapping = aes(x=year, y=value, col=variable))+
  geom_line()+
  theme_bw()+
  xlab('')+
  ylab('')

# Total fair value of the asset and the market value of the equity (need the market value of equity) (iv)

dataFig %>% 
  group_by(year) %>% 
  summarise(
    `Median`=median(FVA_TCE),
    `25th Percentile` = quantile(FVA_TCE, probs = 0.25),
    `75th Percentile` = quantile(FVA_TCE, probs = 0.75)
  ) %>% 
  ungroup() %>% 
  pivot_longer(cols = -year,names_to = "variable",values_to = "value") %>% 
  ggplot(mapping = aes(x=year, y=value, col=variable))+
  geom_line()+
  theme_bw()+
  xlab('')+
  ylab('')


```


## Regression analysis

### Proposition 1: Elasticity of bank activity with respect to bank capital 

```{r}
# model results

q1modeli <- plm(formula = log(TA)~log(TCE),model = 'within',data = data)
q1modelii <- plm(formula = log(TA)~log(TCE)+ROA,model = 'within',data = data)
q1modeliii <- plm(formula = log(TA)~log(TCE)+ROA,model = 'within',index = c('bankID'), data = data)
q1modeliv <- plm(formula = log(TA)~log(TCE)+ROA,model = 'within',index = c('bankID','year'),data = data)
q1modelv <- plm(formula = log(TA)~log(TCE)+ROA,model = 'within',effect = 'twoways',index = c('bankID','year'),data = data)


# compiling the results
result1 <- stargazer(q1modeli,q1modelii,q1modeliii,q1modeliv,q1modelv, type = 'text',
          omit.summary.stat = 'mean',header = FALSE,
          digits = 3)
result1

# coeftest
lmtest::coeftest(q1modeli,vcovHC(q1modeli,type = 'HC0',cluster = 'group'))

# serial correlation method
pbgtest(q1modeli,order = 1)
pbgtest(q1modelii,order = 1)
pbgtest(q1modeliii,order = 1)
pbgtest(q1modeliv,order = 1)
pbgtest(q1modelv,order = 1)


```


### Proposition 2: How does equity react to changes in the business and financial cycle?

* growth rate of common equity == gdp growth+lag(common equity growth)+ROA+IFRS, index=('bankID') ------(i)
* growth rate of common equity == stock market growth + lag(common equity growth)+ROA+IFRS, index=('bankID')------(ii)
* growth rate of common equity == gdp growth:crisis_II+lag(common equity growth)+ROA+IFRS, index=('bankID') ------(iii)
* growth rate of common equity == stock market growth:crisis_II+lag(common equity growth)+ROA+IFRS, index=('bankID') ------(iv)

 
* growth rate of Tier 1 capital == gdp growth+lag( growth rate of Tier 1 capita)+ROA+IFRS, index=('bankID') ------(i)
* growth rate of Tier 1 capital == stock market growth +lag( growth rate of Tier 1 capita)+ROA+IFRS, index=('bankID') ------(ii)
* growth rate of Tier 1 capital == gdp growth:crisis_II + lag( growth rate of Tier 1 capita)+ROA+IFRS, index=('bankID')------(iii)
* growth rate of Tier 1 capital == stock market growth:crisis_II +lag( growth rate of Tier 1 capita)+ROA+IFRS, index=('bankID') ------(iv)


```{r}

# models

q2_1modeli <- plm(formula = TCEG~lag(TCEG)+GDPGrowth+ROA+IFRS,
                  index = 'bankID',model = 'within',data = data)

q2_1modelii <- plm(formula = TCEG~lag(TCEG)+SMGSnP500+ROA+IFRS,
                   index = 'bankID',model = 'within',data = data)

q2_1modeliii <- plm(formula = TCEG~lag(TCEG)+GDPGrowth:crisisGfc+ROA+IFRS,
                    index = 'bankID',model = 'within',data = data)

q2_1modeliv <- plm(formula = TCEG~lag(TCEG)+SMGSnP500:crisisGfc+ROA+IFRS,
                   index = 'bankID',model = 'within',data = data)

# results

stargazer(q2_1modeli,q2_1modelii,q2_1modeliii,q2_1modeliv, type = 'text',
          omit.summary.stat = 'mean',
          digits=3)

# serial correlatio test

pbgtest(q2_1modeli,order = 1)
pbgtest(q2_1modelii,order = 1)
pbgtest(q2_1modeliii,order = 1)
pbgtest(q2_1modeliv,order = 1)


# 2nd part -----------------------------------------------------------------------


# Models


q2_2modeli <- plm(formula = TierCapGrowth~lag(TierCapGrowth)+GDPGrowth+ROA+IFRS,
                  index = 'bankID',model = 'within',data = data)

q2_2modelii <- plm(formula = TierCapGrowth~lag(TierCapGrowth)+SMGSnP500+ROA+IFRS,
                   index = 'bankID',model = 'within',data = data)

q2_2modeliii <- plm(formula = TierCapGrowth~lag(TierCapGrowth)+GDPGrowth:crisisGfc+ROA+IFRS,
                    index = 'bankID',model = 'within',data = data)

q2_2modeliv <- plm(formula = TierCapGrowth~lag(TierCapGrowth)+SMGSnP500:crisisGfc+ROA+IFRS,
                   index = 'bankID',model = 'within',data = data)


# results

stargazer(q2_2modeli,q2_2modelii,q2_2modeliii,q2_2modeliv, type = 'text',
          omit.summary.stat = 'mean',
          digits = 3)


# serial correlation test

pbgtest(q2_2modeli,order = 1)
pbgtest(q2_2modelii,order = 1)
pbgtest(q2_2modeliii,order = 1)
pbgtest(q2_2modeliv,order = 1)

# Hensen Test is required (to be done)




```

### Proposition 3: Impact of bank capitalisation on funding costs


```{r}


# without macroVar ---------------------------------------------------------------

q3_1modeli <- plm(formula = FundingCost~lag(FundingCost)+lag(TA_TE)
                  +ROA +factor(IFRS),
                  index = c('bankID','year'),
                  model = 'fd',
                  data = data)

q3_1modelii <- plm(formula = FundingCost~lag(FundingCost)+lag(RWA_TierCap)
                   +ROA+factor(IFRS),
                   index = c('bankID','year'),
                   model = 'fd',data = data)

# 2nd part (with macro variables) -------------------------------------------------


q3_2modeli <- plm(formula = FundingCost~lag(FundingCost)+lag(TA_TE)
                  +GDPGrowth+SMGSnP500
                  +ROA +factor(IFRS),
                  index = c('bankID','year'),
                  model = 'fd',
                  data = data)

q3_2modelii <- plm(formula = FundingCost~lag(FundingCost)+lag(RWA_TierCap)
                   +GDPGrowth+SMGSnP500
                   +ROA+factor(IFRS),
                   index = c('bankID','year'),
                   model = 'fd',data = data)

q3_2modeliii <- plm(formula = FundingCost~lag(FundingCost)+lag((TCE/TA)*100)
                   +GDPGrowth+SMGSnP500
                   +ROA+factor(IFRS),
                   index = c('bankID','year'),
                   model = 'fd',data = data)


stargazer(q3_1modeli, q3_1modelii, q3_2modeli, q3_2modelii, q3_2modeliii,
          type = 'text',
          omit.summary.stat = 'mean',
          digits = 3)

pbgtest(q3_1modeli,order = 1)
pbgtest(q3_1modelii,order = 1)
pbgtest(q3_2modeli,order = 1)
pbgtest(q3_2modelii,order = 1)
pbgtest(q3_2modeliii,order = 1)




```

### Proposition 4: Do less leveraged banks get more funding?

```{r}


# without macroVar ---------------------------------------------------------------

q4_1modeli <- plm(formula = TFundGrow~lag(TFundGrow)+lag(TA_TE)+ROA+factor(IFRS),
                  index = c('bankID','year'),
                  model = 'within',
                  data = data)
q4_1modelii <- plm(formula = TFundGrow~lag(TFundGrow)+lag(RWA_TierCap)+ROA+factor(IFRS),
                   index = c('bankID','year'),
                   model = 'within',
                   data = data)

# 2nd part (with macro variables) -------------------------------------------------


q4_2modeli <- plm(formula = TFundGrow~lag(TFundGrow)+lag(TA_TE)
                  +GDPGrowth+SMGSnP500+ROA+factor(IFRS),
                  index = c('bankID','year'),
                  model = 'within',
                  data = data)

q4_2modelii <- plm(formula = TFundGrow~lag(TFundGrow)+lag(RWA_TierCap)
                   +GDPGrowth+SMGSnP500+ROA+factor(IFRS),
                   index = c('bankID','year'),
                   model = 'fd',data = data)

stargazer(q4_1modeli, q4_1modelii, q4_2modeli, q4_2modelii,
          type = 'text',
          omit.summary.stat = 'mean',
          digits = 3)

pbgtest(q4_1modeli,order = 1)
pbgtest(q4_1modelii,order = 1)
pbgtest(q4_2modeli,order = 1)
pbgtest(q4_2modelii,order = 1)




```

### Proposition 5: Do less leveraged banks supply more credit?

```{r}

# without macroVar ---------------------------------------------------------------

q5_1modeli <- plm(formula = LG~lag(LG)+lag(TA_TE)+ROA+factor(IFRS),
                  index = c('bankID','year'),
                  model = 'within',
                  data = data)
q5_1modelii <- plm(formula = LG~lag(LG)+lag(RWA_TierCap)+ROA+factor(IFRS),
                   index = c('bankID','year'),
                   model = 'within',
                   data = data)

# 2nd part (with macro variables) -------------------------------------------------


q5_2modeli <- plm(formula = LG~lag(LG)+lag(TA_TE)+ROA+factor(IFRS)
                  +GDPGrowth+SMGSnP500,
                  index = c('bankID','year'),
                  model = 'within',
                  data = data)

q5_2modelii <- plm(formula = LG~lag(LG)+lag(RWA_TierCap)+ROA+factor(IFRS)
                   +GDPGrowth+SMGSnP500,
                   index = c('bankID','year'),
                   model = 'fd',data = data)

stargazer(q5_1modeli, q5_1modelii, q5_2modeli, q5_2modelii,
          type = 'text',
          omit.summary.stat = 'mean',
          digits = 3)

pbgtest(q5_1modeli,order = 1)
pbgtest(q5_1modelii,order = 1)
pbgtest(q5_2modeli,order = 1)
pbgtest(q5_2modelii,order = 1)

```



### Proposition: 07: The effect of bank capital in the monetary transmission mechanism

```{r}

# without macroVar ---------------------------------------------------------------

q6_1modeli <- plm(formula = LG~lag(LG)+lag(TA_TE)+(lag(TA_TE)*MPGrowth),
                  index = c('bankID','year'),
                  model = 'within',
                  data = data)
q6_1modelii <- plm(formula = LG~lag(LG)+lag(RWA_TierCap)+(lag(RWA_TierCap)*MPGrowth),
                   index = c('bankID','year'),
                   model = 'within',
                   data = data)

# 2nd part (with macro variables) -------------------------------------------------


q6_2modeli <- plm(formula = LG~lag(LG)+lag(TA_TE)+(lag(TA_TE)*MPGrowth)+
                    ROA+factor(IFRS)+
                    GDPGrowth+SMGSnP500,
                  index = c('bankID','year'),
                  model = 'within',
                  data = data)

q6_2modelii <- plm(formula = LG~lag(LG)+lag(RWA_TierCap)+(lag(RWA_TierCap)*MPGrowth)+
                     ROA+factor(IFRS)
                   +GDPGrowth+SMGSnP500,
                   index = c('bankID','year'),
                   model = 'within',data = data)

stargazer(q6_1modeli, q6_1modelii, q6_2modeli, q6_2modelii,
          type = 'text',
          omit.summary.stat = 'mean',
          digits = 3)

pbgtest(q6_1modeli,order = 1)
pbgtest(q6_1modelii,order = 1)
pbgtest(q6_2modeli,order = 1)
pbgtest(q6_2modelii,order = 1)



```



